---
editor_options:
  chunk_output_type: console
fontsize: 12pt
geometry: margin=1in
header-includes: \usepackage{float} \usepackage{lineno} \renewcommand{\thepage}{S\arabic{page}}
  \renewcommand{\thesection}{Appendix S\arabic{section}} \renewcommand{\thetable}{S\arabic{table}}
  \renewcommand{\thefigure}{S\arabic{figure}}
  \usepackage{amsmath}
  \renewcommand{\theequation}{S\arabic{equation}} \floatplacement{figure}{H} \renewcommand*\oldstylenums[1]{\textosf{#1}}
  \usepackage{tocloft} \addtolength{\cftsecnumwidth}{70pt} \setcounter{tocdepth}{1}
  \usepackage[round]{natbib}  \bibpunct[:]{(}{)}{,}{a}{}{;}
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  word_document: default
---

2020
\vspace{1cm}

\begin{centering}
 \textbf{Supplementary Material: Catastrophes, connectivity, and Allee effects in the design of marine reserve networks}
 
 \vspace{2 mm}
 
Easton R. White,$^{1,2\ast}$ Marissa L. Baskett,$^{2,3}$, Alan Hastings$^{2,3,4}$

\normalsize{$^{1}$Department of Biology, University of Vermont, Burlington, VT, USA \\$^{2}$Center for Population Biology, University of California, Davis, CA, USA, \\
$^{3}$Department of Environmental Science and Policy, University of California, Davis, CA, USA \\
$^{4}$Santa Fe Institute, Sante Fe, NM, USA}

\normalsize{$^\ast$To whom correspondence should be addressed: E-mail:  eastonrwhite@gmail.com}


\vspace{2 mm}

\end{centering}

\vspace{2 mm}

\tableofcontents

\vspace{1cm}

Data and code for all the figures and tables can be found at (https://github.com/eastonwhite/MPA-disturbances). 


\clearpage

# $n$-patch model description


To extend the two-patch model described in the main manuscript to an $n$-patch scenario, we have to use a slightly different model formulation. We use the same Beverton-Holt structure within each patch for production described in the main manuscript. However, we model spatially-explicit dispersal (i.e.\ resulting connectivity between patches) and disturbances. We focus on a coastline system (a simple one-dimensional landscape) where $d_{ij}$ is the distance between patches $i$ and $j$ (also see Figure 1d in main text). Thus, the patches are in a contiguous line and where discrete patches next to each other would have a distance of $d_{ij}=1$ between them. 

We use geometric decay for the dispersal kernel, with a dispersal shape parameter $\delta$, where increasing $\delta$ decreases dispersal amount and distance. The probability of dispersal from patch $i$ to $j$ is

\begin{equation}
P(\mbox{dispersal from patch i to patch j}) = \text{Geometric}(\delta,d_{ij}).
\end{equation}


For disturbances, we model the probability of disturbance, $M_i$, in each patch as a binomial process with probability $p_i$: 
\begin{equation}
M_i(t)  \sim \text{Binomial}(1, p_i).
\end{equation}
The spatial extent of the disturbance is a stochastic process giving the disturbance size ($x$), which affects patches near the disturbance. If a disturbance in patch $i$ is larger than the distance between patches $i$ and $j$, $d_{ij}$, then patch $j$ will also be affected by the disturbance:
\begin{equation}
P(\mbox{disturbance in patch j } | \mbox{ disturbance in patch i}) =
\begin{cases}
1       & \quad \text{if } d_{ij} < x\\
0  & \quad \text{if } \text{ otherwise}.
\end{cases}
\end{equation}

A disturbance causes density-independent mortality, $\mu$, for the entire patch and all patches with distance $x$.

<!--
\begin{equation}
P(\mbox{disturbance of size x})  \sim \text{Exponential}(-\lambda x)
\end{equation}
-->




With this $n$-patch model, we can relax the assumption of a "scorched earth" between patches by setting the fraction of biomass fished in non-reserves to be $F<1$. This allows us to study the effect of fishing pressure outside reserves on the effectiveness of the marine reserve network.



\begin{table}[]
\begin{tabular}{|p{1.5cm} | p{10cm} | p{3cm}|}
\hline 
Notation & Description & Default value(s) \\ \hline \hline
$r_i(t)$             & growth factor of patch $i$ at time $t$ described as a normal distribution       &       \\ \hline
$\mu_r$              & mean of growth factor normal distribution            & 3      \\ \hline
$\sigma_r^2$        & variance of growth factor normal distribution        &  0.5     \\ \hline
$K_i$                & carrying capacity for patch $i$           & 1      \\ \hline
$\omega$            & Allee effect parameter             & 1 for no Allee effect or $>$1 for Allee effect   \\ \hline
$\delta$             & dispersal kernel shape parameter (larger $\delta$ indicates less dispersal)            &  0.7     \\ \hline
$p_i$                & probability of disturbance            & 0.02       \\ \hline
$x$             & size of disturbance (number of patches adjacent to disturbed patch that will also be disturbed)           & 1        \\ \hline
$\mu$                & density-independent mortality from disturbance           & 0.9      \\ \hline
$F$                & fraction of biomass fished in non-reserves         & for scorched earth assumption of all biomass caught or $<$1 for moderate levels of fishing      \\ \hline
\end{tabular}
\caption{Parameter notation, description, and default values for the n-patch model. As a sensitivity analysis, several parameters are varied in the Figs. 5,6, S4. \label{tab:parameters}} 
\end{table}



<!--
\section{Growth functions}

```{r,echo=F,eval=F,cache=T,error=F,message=F,warning=F,fig.cap="Growth functions for population size from year t to year t+1. Each panel represents a different combination of the intrinsic rate of increase (r) and the Allee parameter ($\\omega$). This is for the two-patch model.\\label{fig:growth_functions}"}


plot_reproductive_function = function(r,omega,K){

curve((r*x^omega)/(1 + (x^omega)/K) ,from=0,to=2,ylab='N(t+1)',xlab='N(t)',
      ylim=c(0,4),xlim=c(0,4),las=1)
#curve(-1+(r*x^omega)/(1 + (x^omega)/K)/x ,from=-3,to=2,ylab='Growth rate',xlab='N(t)',
 #    ylim=c(-1,1),xlim=c(0,2),las=1)
#abline(h=0)
abline(coef = c(0,1),lty=2)


#bv_function <- function(x,r,omega) x - r*(x^omega)/(1+(x^omega))
#allee_threshold <- uniroot(bv_function,r=r,omega=omega,interval=c(0.0001,0.9))$root
#abline(v=allee_threshold,col='blue',lty=2)
}

par(mfrow=c(2,2),oma=c(4,4,2.5,1),mar=c(2,2,0.5,1))
plot_reproductive_function(2,1,1)
mtext(text = bquote(omega == 1),side = 3,line = 1,cex=1.2)
mtext(text = bquote(r == 2),side = 2,line = 4,cex=1.2)
plot_reproductive_function(2,1.5,1)
mtext(text = bquote(omega == 1.5),side = 3,line = 1,cex=1.2)

plot_reproductive_function(2.5,1,1)
mtext(text = bquote(r == 2.5),side = 2,line = 4,cex=1.2)
plot_reproductive_function(2.5,1.5,1)

mtext(text = 'N(t)',side = 1,line = 1,outer = T,cex=1.4)
mtext(text = 'N(t+1)',side = 2,line = 1,outer=T,cex=1.4)
```
-->

\clearpage

# Additional figures


```{r,eval=T,echo=F,cache=T,error=F,message=F,warning=F,fig.cap="Optimal spacing for varying Allee and r values along with different disturbance parameters.\\label{fig:allee_and_r}"}
source('../scripts/two_patch/find_optimal_spacing_two_patch.R')

# optimal spacing versus prob disturbance for different Allee and r values

require(ggplot2)
require(viridis)


prob_vector = seq(0.001,1,by=0.2)
#(-1/50)*log(prob_vector)
K1 = 1
r1_vector = seq(2,3,0.5)
epsilon_vec = 0.5#seq(0.1,0.7,0.25)
gamma_vector = 0.1#(-1/50)*log(prob_vector)#log(seq(0.0001,0.1,by=0.005))
delta_vector = 0.01#(-1/50)*log(prob_vector)#log(seq(0.0001,0.05,0.005))

prob_disturb_vec =seq(0,0.3,0.1)
severity_disturb_vec = c(0.1,0.3,0.5)
omega_vec = c(1,1.3,1.6)

params_to_try = expand.grid(r1_vector,epsilon_vec,gamma_vector,delta_vector,prob_disturb_vec,severity_disturb_vec,omega_vec)
names(params_to_try) <- c("r1_vector","epsilon_vec","gamma_vector","delta_vector","prob_disturb_vec","severity_disturb_vec","omega_vec")


optimal_spacing = vector('numeric',nrow(params_to_try))
prob_persistence = vector('numeric',nrow(params_to_try))
for (param_trial in 1:nrow(params_to_try)){
  optimal_spacing_output = find_optimal_spacing(params_to_try$r1_vector[param_trial],K1,params_to_try$delta_vector[param_trial],params_to_try$epsilon_vec[param_trial],params_to_try$omega_vec[param_trial],params_to_try$prob_disturb_vec[param_trial], params_to_try$severity_disturb_vec[param_trial],params_to_try$gamma_vector[param_trial])
  optimal_spacing[param_trial]=optimal_spacing_output[1]
  prob_persistence[param_trial]=(1-optimal_spacing_output[2])
  #print(param_trial)
}



myoutput <- data.frame(params_to_try,optimal_spacing,prob_persistence)
myoutput$severity_disturb_vec = 1 - myoutput$severity_disturb_vec

ggplot(aes(x=prob_disturb_vec,y=optimal_spacing,shape=as.factor(severity_disturb_vec),color=prob_persistence),data=myoutput) + geom_line() + geom_point() + facet_grid(rows = vars(omega_vec), cols = vars(r1_vector))+
   scale_color_viridis(discrete=FALSE,begin = 0.2,end=0.8) +
   labs(color='Probability of persistence',shape = 'Disturbance mortality rate') +
   xlab("Probability of disturbance") +
   ylab("Optimal spacing between reserves") +
   theme_classic(base_size = 14, base_family = "")


#mm=lm(myoutput$optimal_spacing~myoutput$prob_disturb_vec*myoutput$severity_disturb_vec*myoutput$omega_vec)
#summary(mm)
```






```{r,eval=T,echo=F,cache=T,error=F,message=F,warning=F,fig.cap="Optimal spacing for different $\\gamma$, $\\delta$, r, and probability of disturbance.\\label{fig:disturb_vs_dispersal}"}
source('../scripts/two_patch/find_optimal_spacing_two_patch.R')

# optimal spacing versus prob disturbance for different disperer and r values.

require(ggplot2)
require(viridis)


prob_vector = seq(0.001,1,by=0.2)
#(-1/50)*log(prob_vector)
K1 = 1
r1_vector = seq(2.5,3,0.5)
epsilon_vec = 0.7#seq(0.1,0.7,0.25)
gamma_vector = (-1/50)*log(prob_vector)#log(seq(0.0001,0.1,by=0.005))
delta_vector = (-1/50)*log(prob_vector)#log(seq(0.0001,0.05,0.005))

prob_disturb_vec = 0.05#seq(0,0.3,0.05)
severity_disturb_vec = 0.1#c(0.1,0.3,0.5)
omega_vec = 1.2#c(1,1.2,1.4)

params_to_try = expand.grid(r1_vector,epsilon_vec,gamma_vector,delta_vector,prob_disturb_vec,severity_disturb_vec,omega_vec)
names(params_to_try) <- c("r1_vector","epsilon_vec","gamma_vector","delta_vector","prob_disturb_vec","severity_disturb_vec","omega_vec")


optimal_spacing = vector('numeric',nrow(params_to_try))
prob_persistence = vector('numeric',nrow(params_to_try))
for (param_trial in 1:nrow(params_to_try)){
  optimal_spacing_output = find_optimal_spacing(params_to_try$r1_vector[param_trial],K1,params_to_try$delta_vector[param_trial],params_to_try$epsilon_vec[param_trial],params_to_try$omega_vec[param_trial],params_to_try$prob_disturb_vec[param_trial], params_to_try$severity_disturb_vec[param_trial],params_to_try$gamma_vector[param_trial])
  optimal_spacing[param_trial]=optimal_spacing_output[1]
  prob_persistence[param_trial]=(optimal_spacing_output[2])
  #print(param_trial)
}



myoutput <- data.frame(params_to_try,optimal_spacing,prob_persistence)
myoutput$delta_vector = exp(-myoutput$delta_vector*50)
myoutput$gamma_vector = exp(-myoutput$gamma_vector*50)

ggplot(aes(x=delta_vector,y=optimal_spacing,color=prob_persistence,shape=as.factor(round(gamma_vector,4))),data=myoutput) + geom_point(alpha=0.8,size=1.5) + facet_wrap(~r1_vector) +
   labs(color = 'Probability of persistence', shape = 'Probability disturbance spreads') +
   scale_color_viridis(discrete=FALSE,begin = 0.2,end=0.8) +
   xlab("Probability of successful dispersal") +
   ylab("Optimal spacing between reserves") +
   theme_classic(base_size = 14, base_family = "")

```





```{r,echo=F,eval=T,cache=T,error=F,message=F,warning=F,fig.cap="Optimal spacing for all the dispersal parameters and the probability of disturbance.\\label{fig:dispersal_params}"}
source('../scripts/two_patch/find_optimal_spacing_two_patch.R')

# optimal spacing versus prob disturbance for different Allee and r values

require(ggplot2)
require(viridis)


prob_vector = seq(0.001,1,by=0.1)
#(-1/50)*log(prob_vector)
K1 = 1
r1_vector = 2#seq(0.5,3,0.5)
epsilon_vec = c(0.25,0.75)
gamma_vector = (-1/50)*log(prob_vector)#log(seq(0.0001,0.1,by=0.005))
delta_vector = (-1/50)*log(prob_vector)#log(seq(0.0001,0.05,0.005))

prob_disturb_vec = 0.1#seq(0,0.3,0.05)
severity_disturb_vec = 0.1#c(0.1,0.3,0.5)
omega_vec = c(1,1.2)

params_to_try = expand.grid(r1_vector,epsilon_vec,gamma_vector,delta_vector,prob_disturb_vec,severity_disturb_vec,omega_vec)
names(params_to_try) <- c("r1_vector","epsilon_vec","gamma_vector","delta_vector","prob_disturb_vec","severity_disturb_vec","omega_vec")


optimal_spacing = vector('numeric',nrow(params_to_try))
prob_persistence = vector('numeric',nrow(params_to_try))
for (param_trial in 1:nrow(params_to_try)){
  optimal_spacing_output = find_optimal_spacing(params_to_try$r1_vector[param_trial],K1,params_to_try$delta_vector[param_trial],params_to_try$epsilon_vec[param_trial],params_to_try$omega_vec[param_trial],params_to_try$prob_disturb_vec[param_trial], params_to_try$severity_disturb_vec[param_trial],params_to_try$gamma_vector[param_trial])
  optimal_spacing[param_trial]=optimal_spacing_output[1]
  prob_persistence[param_trial]=(100-optimal_spacing_output[2])
 # print(param_trial)
}



myoutput <- data.frame(params_to_try,optimal_spacing,prob_persistence)
myoutput$delta_vector = round(exp(-myoutput$delta_vector*50),4)
myoutput$gamma_vector = round(exp(-myoutput$gamma_vector*50),4)

#myoutput <- subset(myoutput,myoutput$epsilon_vec==0.4)

ggplot(aes(x=gamma_vector,y=delta_vector,fill=optimal_spacing),data=myoutput) + geom_tile() + facet_grid(vars(omega_vec),vars(epsilon_vec))+
   scale_color_viridis(discrete=FALSE,begin = 0.2,end=0.8) +
   labs(fill='Optimal spacing') +
   xlab("Probability of disturbance in second patch") +
   ylab("Probability of successful dispersal") +
   theme_classic(base_size = 14, base_family = "")


#mm=lm(myoutput$optimal_spacing~myoutput$prob_disturb_vec*myoutput$severity_disturb_vec*myoutput$omega_vec)
#summary(mm)
```



















<!-- n-patch model runs -->






<!--
```{r biased_disturbance, echo=FALSE,eval=FALSE,cache=TRUE,error=FALSE,message=FALSE,warning=FALSE,fig.cap='...\\label{biased_disturbance}'}

# Show effects of disturbances not uniformly distributed....

# Place reserves in one-third of landscape then in 1 of every three randomly distributed...Where should reserves then go?

# Make plot of fraction of reserves situated in disturbed areas for different parameter values

# Need to modify disturbance code to do this properly. Currently the code just says no disturbances happen in certain areas. But for not unbiased cases, this means the disturbance rates are much higher...

biased_disturbance_side = FALSE
biased_disturbance_rotating = FALSE
source('big_loop.R')

biased_disturbance_side = FALSE
biased_disturbance_rotating = TRUE
source('big_loop.R')

biased_disturbance_side = TRUE
biased_disturbance_rotating = FALSE
source('big_loop.R')

# So far it looks like you should only protect areas that aren't disturbed. This makes some sense. Would this change if we didn't have a scorched Earth assumption?

```
-->




```{r reserve_percent,echo=FALSE,eval=T,cache=TRUE,error=FALSE,message=FALSE,warning=FALSE,fig.cap='Optimal mean spacing between reserves for different probabilities of disturbance and fraction of coasline in reserves. The specific parameters used here include: $\\delta$ = 0.7, $\\omega$ = 1.2, r = 3, and $\\mu$ = 0.9.\\label{reserve_percent}'}

# Run "big_loop" code with multiple reserve area sizes..
require(viridis)
colors <- viridis(3,begin = 0.2,end=0.8)


biased_disturbance_rotating = FALSE
biased_disturbance_side = FALSE
num_reserves = 2
source('../scripts/n_patch/big_loop.R')
#write.csv(x = params_list,file=paste('params_list',num_reserves,'.csv',sep=''),quote = F,row.names = F)

plot(params_list$disturbance_prob_vec,params_list$optimal_spacing-1,type='l',lwd=3,ylab='Optimal spacing between reserves',xlab="Probability of disturbance",cex.lab=1.3,ylim=c(0,6),las=1,col=colors[1],lty=1)

num_reserves = 3
source('../scripts/n_patch/big_loop.R')
#write.csv(x = params_list,file=paste('params_list',num_reserves,'.csv',sep=''),quote = F,row.names = F)
points(params_list$disturbance_prob_vec,params_list$optimal_spacing-1,type='l',lwd=3,ylab='Mean spacing in optimal reserve network',xlab="Probability of disturbance",cex=1.3,col=colors[2],lty=2)

 num_reserves = 4
 source('../scripts/n_patch/big_loop.R')
 #write.csv(x = params_list,file=paste('params_list',num_reserves,'.csv',sep=''),quote = F,row.names = F)
 points(params_list$disturbance_prob_vec,params_list$optimal_spacing-1,type='l',lwd=3,ylab='Mean spacing in optimal reserve network',xlab="Probability of disturbance",cex.lab=1.3,col=colors[3],lty=3)
 
 # num_reserves = 5
 # source('../scripts/n_patch/big_loop.R')
 # #write.csv(x = params_list,file=paste('params_list',num_reserves,'.csv',sep=''),quote = F,row.names = F)
 # points(params_list$disturbance_prob_vec,params_list$optimal_spacing-1,type='l',lwd=3,ylab='Mean spacing in optimal reserve network',xlab="Probability of disturbance",cex.lab=1.3,col=colors[4],lwd=2) 
# 
# 


legend('topright',legend = c('0.17','0.25','0.33'),col = colors,pch = 16,lwd=2,lty=1:3)

```



