---
fontsize: 12pt
geometry: margin=1in
header-includes:
  \usepackage{float}
  \usepackage{lineno}
  \usepackage{setspace}\doublespacing
  \usepackage{color}
  \setcounter{figure}{1}
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: no
  word_document: default
editor_options:
  chunk_output_type: console
---
<!--Running head: Power to detect population trends-->

\pagenumbering{gobble}

Figures for: Catastrophes, connectivity, and Allee effects in the design of marine reserve networks
\vspace{7 mm}

Easton R. White,$^{1,2\ast}$ Marissa L. Baskett,$^{2,3}$, Alan Hastings$^{2,3,4}$

\normalsize{$^{1}$Department of Biology, University of Vermont, Burlington, VT, USA \\$^{2}$Center for Population Biology, University of California, Davis, CA, USA, \\
$^{3}$Department of Environmental Science and Policy, University of California, Davis, CA, USA \\
$^{4}$Santa Fe Institute, Sante Fe, NM, USA}

\normalsize{$^\ast$To whom correspondence should be addressed: E-mail:  eastonrwhite@gmail.com}

\vspace{2 mm}

\clearpage


```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```


## Figure 2

```{r pop-dyn, echo=F,eval=T,error=FALSE,message=F,warning=FALSE,fig.cap='Example two-patch model simulation, each line denotes a different patch. The four panels represent different combinations of disturbance frequency and the presence (\\(\\omega>1\\)) or absence of an Allee effect. The horizontal line denotes the Allee threshold. The simulation is with the following model parameters: \\(r = 2.0\\) , \\(K=1\\), \\(\\delta = 0.01\\), \\(\\epsilon = 0.5\\), and distance between patches of 40.  \\label{fig:pop-dyn}',fig.height=5}
#parameters

source('../scripts/two_patch/simulate_model.R')
set.seed(123)
par(mfcol=c(2,2),mar=c(2,0,0.5,0.5),oma=c(2,4,1,0))


source('../scripts/two_patch/parameter_values_two_patch.R')
distance=10

time_series = simulate_model(r1,K1,delta,epsilon,omega,prob_disturb, severity_disturb, gamma, distance,output_time_series = TRUE)
N1 = time_series[1,]
N2 = time_series[2,]


plot(N1,type='l',ylim=c(0,2.5),xlab='',ylab='',las=1,xaxt='n')
points(N2,type='l',col='red',lty=2)
mtext(text = 'disturbance frequency = 0.02',side = 3,line = -1,adj=0.9)
mtext(text = '(a)',side = 3,line = -1,adj=0.02)
bv_function <- function(x,r1,omega) x - r1*(x^omega)/(1+(x^omega))
mtext(text = expression(paste("No Allee effect ( ", omega, "=1)")),side = 3,line = 0.1,at = 50)

####
#parameters


set.seed(123)
prob_disturb=0.3
time_series = simulate_model(r1,K1,delta,epsilon,omega,prob_disturb, severity_disturb, gamma, distance,output_time_series = TRUE)
N1 = time_series[1,]
N2 = time_series[2,]

#par(mfrow=c(1,2))
plot(N1,type='l',ylim=c(0,2.5),xlab='',ylab='',las=1)
points(N2,type='l',col='red',lty=2)
mtext(text = '(b)',side = 3,line = -1,adj=0.02)
mtext(text = 'disturbance frequency = 0.30',side = 3,line = -1,adj=0.9)
mtext(text = 'Time (years)',side = 1,line = 0.5,outer = T,cex = 1.2)
mtext(text = 'Population size',side = 2,line = 2.4,outer = T,cex = 1.2)




# Include Allee effect
set.seed(123)
omega=1.2
prob_disturb=0.02
time_series = simulate_model(r1,K1,delta,epsilon,omega,prob_disturb, severity_disturb, gamma, distance,output_time_series = TRUE)
N1 = time_series[1,]
N2 = time_series[2,]

plot(N1,type='l',ylim=c(0,2.5),xlab='',ylab='',las=1,yaxt='n',xaxt='n')
points(N2,type='l',col='red',lty=2)
mtext(text = '(c)',side = 3,line = -1,adj=0.02)
mtext(text = 'disturbance frequency = 0.02',side = 3,line = -1,adj=0.9)
bv_function <- function(x,r1,omega) x - r1*(x^omega)/(1+(x^omega))
abline(h= uniroot(bv_function,r1=r1,omega=omega,interval=c(0.0001,0.9))$root,col='blue')
mtext(text = expression(paste("Allee effect ( ", omega, "=1.2)")),side = 3,line = 0.1,at = 50)

####
#parameters

set.seed(123)
omega=1.2
prob_disturb=0.3
time_series = simulate_model(r1,K1,delta,epsilon,omega,prob_disturb, severity_disturb, gamma, distance,output_time_series = TRUE)
N1 = time_series[1,]
N2 = time_series[2,]

#par(mfrow=c(1,2))
plot(N1,type='l',ylim=c(0,2.5),xlab='',ylab='',las=1,yaxt='n')
points(N2,type='l',col='red',lty=2)
mtext(text = '(d)',side = 3,line = -1,adj=0.02)
mtext(text = 'disturbance frequency = 0.30',side = 3,line = -1,adj=0.9)
mtext(text = 'Time (years)',side = 1,line = 0.5,outer = T,cex = 1.2)
mtext(text = 'Population size',side = 2,line = 2.4,outer = T,cex = 1.2)
abline(h= uniroot(bv_function,r1=r1,omega=omega,interval=c(0.0001,0.9))$root,col='blue')

legend(x = 50,y = 1.5,legend = c('Patch 1','Patch 2'),col=c(1,2),lty=c(1,2),cex=1.2)

```

\clearpage

## Figure 3

```{r optimal-spacing-simple-model-code, echo=FALSE,eval=F,cache=TRUE, error=FALSE,message=FALSE,warning=FALSE}


# Run models and create output csv files

source('../scripts/two_patch/find_optimal_spacing_two_patch.R')

set.seed(123)

# Parameters
source('../scripts/two_patch/parameter_values_two_patch.R')
source('../scripts/two_patch/simulate_model.R')

prob_vector = rep(seq(0,0.5,by=0.02),5)
severity_vector = c(0.05,0.25,0.5)#c(0.01,0.1,0.25,0.5,0.75)#seq(0.01,0.3,by=0.025)
params_to_try = expand.grid(prob_vector,severity_vector)


optimal_spacing = vector('numeric',nrow(params_to_try))
mean_pop_size = vector('numeric',nrow(params_to_try))
for (param_trial  in 1:nrow(params_to_try)){
  optimal_spacing_output = find_optimal_spacing(r1,K1,delta,epsilon,omega,params_to_try[param_trial,1], params_to_try[param_trial,2], gamma,objective='persistence')
  optimal_spacing[param_trial]=optimal_spacing_output[1]
  mean_pop_size[param_trial]=optimal_spacing_output[2]
  print(param_trial)
}


myoutput <- data.frame(params_to_try,optimal_spacing,mean_pop_size)
names(myoutput) <- c('disturbance_frequency','disturbance_mortality','optimal_spacing','mean_pop_size')
myoutput$disturbance_mortality = 1-myoutput$disturbance_mortality
myoutput$disturbance_mortality=as.factor(myoutput$disturbance_mortality)

write.csv(myoutput,file='../model_outputs/two_patch_optimal_spacing_vs_disturbance_regime_NoAllee_Fig3a.csv',quote = F)



########## MODEL WITH ALLEE EFFECTS

omega=1.2

optimal_spacing = vector('numeric',nrow(params_to_try))
mean_pop_size = vector('numeric',nrow(params_to_try))
for (param_trial in 1:nrow(params_to_try)){
  optimal_spacing_output = find_optimal_spacing(r1,K1,delta,epsilon,omega,params_to_try[param_trial,1], params_to_try[param_trial,2], gamma,objective='persistence')
  optimal_spacing[param_trial]=optimal_spacing_output[1]
  mean_pop_size[param_trial]=optimal_spacing_output[2]
  
  #if (param_trial%%1000 == 0) {print(param_trial)}
  print(param_trial)
}


myoutput <- data.frame(params_to_try,optimal_spacing)
names(myoutput) <- c('disturbance_frequency','disturbance_mortality','optimal_spacing')
myoutput$disturbance_mortality = 1-myoutput$disturbance_mortality
myoutput$disturbance_mortality=as.factor(myoutput$disturbance_mortality)


write.csv(myoutput,file='../model_outputs/two_patch_optimal_spacing_vs_disturbance_regime_WithAllee_Fig3b.csv',quote = F)

```


```{r optimal-spacing-simple-model, echo=FALSE,eval=T,cache=TRUE,fig.height=6, error=FALSE,message=FALSE,warning=FALSE,fig.cap='Optimal spacing for different disturbance frequencies and mortality rates. Optimal spacing for the Beverton-Holt model (a) without ($\\omega=1$) and (b) with an Allee effect ($\\omega=1.2$). Each line indicates a different disturbance mortality rate. These simulations are with the same model parameters as in Fig. 2.\\label{optimal-spacing-simple-model}'}

model_output <- read.csv(file='../model_outputs/two_patch_optimal_spacing_vs_disturbance_regime_NoAllee_Fig3a.csv',header=T)

require(dplyr)

model_output <- model_output %>%
  dplyr::group_by(disturbance_frequency,disturbance_mortality) %>%
  dplyr::summarise(avg_optimal_spacing = mean(optimal_spacing),avg_optimal_spacing2.5 = as.numeric(quantile(optimal_spacing,probs=0.025)),avg_optimal_spacing97.5 = as.numeric(quantile(optimal_spacing,probs=0.975)))

require(ggplot2)
require(viridis)
require(gridExtra)
p1 <- ggplot(data=model_output) +
   geom_ribbon(aes(x=disturbance_frequency,ymin=avg_optimal_spacing2.5,ymax=avg_optimal_spacing97.5 ,fill=as.factor(disturbance_mortality))) + scale_fill_viridis(discrete=T,alpha=0.1,guide=F) +
   geom_line(aes(x=disturbance_frequency,y=avg_optimal_spacing,color=as.factor(disturbance_mortality)),size=1.5) + scale_color_viridis(discrete = T,alpha=0.5)   + theme_classic(base_size = 14, base_family = "")  + coord_cartesian(xlim = c(0, 0.5),ylim = c(0, 50)) + theme(plot.title = element_text(size = 12, face = "plain")) +
  labs(col='Disturbance mortality rate') +
  xlab(" ") +
  ylab(" ") +
  ggtitle("No Allee effect") +
  theme(legend.position="none") +
 # annotate("text",x=0.35,y=10,label='Small disturbance',col='black') +
 # annotate("text",x=0.25,y=50,label='Large disturbance',col='black')+
  annotate("text",x=0.48,y=48,label='(a)',col='black')


########## MODEL WITH ALLEE EFFECTS

model_output <- read.csv(file='../model_outputs/two_patch_optimal_spacing_vs_disturbance_regime_WithAllee_Fig3b.csv',header=T)

require(dplyr)

model_output <- model_output %>%
  dplyr::group_by(disturbance_frequency,disturbance_mortality) %>%
  dplyr::summarise(avg_optimal_spacing = mean(optimal_spacing),avg_optimal_spacing2.5 = as.numeric(quantile(optimal_spacing,probs=0.025)),avg_optimal_spacing97.5 = as.numeric(quantile(optimal_spacing,probs=0.975)))

require(ggplot2)
require(viridis)
require(gridExtra)
p2 <- ggplot(data=model_output) +
   geom_ribbon(aes(x=disturbance_frequency,ymin=avg_optimal_spacing2.5,ymax=avg_optimal_spacing97.5 ,fill=as.factor(disturbance_mortality))) + scale_fill_viridis(discrete=T,alpha=0.1,guide=F) +
   geom_line(aes(x=disturbance_frequency,y=avg_optimal_spacing,color=as.factor(disturbance_mortality)),size=1.5) + scale_color_viridis(discrete = T,alpha=0.5)   + theme_classic(base_size = 14, base_family = "")  + coord_cartesian(xlim = c(0, 0.5),ylim = c(0, 50)) + theme(plot.title = element_text(size = 12, face = "plain")) +
  labs(col='Disturbance mortality rate') +
  xlab(" ") +
  ylab(" ") +
  ggtitle("Allee effect") +
  theme(legend.position="none") +
 # annotate("text",x=0.35,y=10,label='Small disturbance',col='black') +
 # annotate("text",x=0.25,y=50,label='Large disturbance',col='black')+
  annotate("text",x=0.48,y=48,label='(b)',col='black')


library(ggpubr)

#pdf(file = 'figures/two_patch_optimal_spacing.pdf',width=8,height=5)
figure=ggarrange(p1, p2, ncol=1, nrow=2, common.legend = TRUE, legend="top")
annotate_figure(figure,
               bottom = text_grob("Disturbance frequency", color = "black",
                          hjust = 0.5,vjust=-1, x = 0.5, size = 14),
               left = text_grob("Optimal spacing between reserves", color = "black", rot = 90,size=14,vjust=2,hjust=0.4)
)
#dev.off()
```


\clearpage





## Figure 4

```{r gamma_vs_delta2_code, echo=FALSE,eval=F,cache=TRUE, error=FALSE,message=FALSE,warning=FALSE,fig.cap='The optimal spacing between reserves for population persistence given different combinations of successful dispersal probability (to a patch 50 units away) and the probability that a disturbance in one patch affects the nearby second patch (at a distance of 50 units away). Simulations here are for a two-patch model (a) without and (b) with an Allee effect and the same parameter values as in figure 2.\\label{gamma_vs_delta}'}


# Parameters
source('../scripts/two_patch/parameter_values_two_patch.R')
source('../scripts/two_patch/parameter_values_two_patch.R')
source('../scripts/two_patch/simulate_model.R')

prob_vector = rep(seq(0.001,1,by=0.05),5)
#(-1/50)*log(prob_vector)


omega=1.2
severity_disturb = 0.05
epsilon = 0.25


gamma_vector = (-1/50)*log(prob_vector)#log(seq(0.0001,0.1,by=0.005))
delta_vector = (-1/50)*log(prob_vector)#log(seq(0.0001,0.05,0.005))
params_to_try = expand.grid(gamma_vector,delta_vector)


optimal_spacing = vector('numeric',nrow(params_to_try))
mean_pop_size = vector('numeric',nrow(params_to_try))
for (param_trial in 1:nrow(params_to_try)){
  optimal_spacing_output = find_optimal_spacing(r1,K1,params_to_try[param_trial,2],epsilon,omega,0.1, 0.25, params_to_try[param_trial,1],objective='persistence')
  optimal_spacing[param_trial]=optimal_spacing_output[1]
  mean_pop_size[param_trial]=optimal_spacing_output[2]
  #print(param_trial)
}

myoutput <- data.frame(params_to_try,optimal_spacing,mean_pop_size)
names(myoutput) <- c('gamma','delta','optimal_spacing','mean_pop_size')

myoutput$delta = exp(-myoutput$delta*50)
myoutput$gamma = exp(-myoutput$gamma*50)

write.csv(myoutput,file='../model_outputs/two_patch_optimal_spacing_for_dispersal_vs_disturbance_Fig4.csv',quote = F)
```


```{r gamma_vs_delta2, echo=FALSE,eval=T, error=FALSE,message=FALSE,warning=FALSE,fig.cap='The optimal spacing between reserves for population persistence given different combinations of successful dispersal probability (to a patch 50 units away) and the probability that a disturbance in one patch affects the nearby second patch (at a distance of 50 units away). Simulations here are for a two-patch model (a) without and (b) with an Allee effect and the same parameter values as in figure 2.\\label{gamma_vs_delta}'}

model_output <- read.csv(file='../model_outputs/two_patch_optimal_spacing_for_dispersal_vs_disturbance_Fig4.csv',header=T)

require(dplyr)
require(ggplot2)
require(viridis)
model_output  <- model_output %>%
  dplyr::group_by(gamma,delta) %>%
  dplyr::summarise(avg_optimal_spacing = mean(optimal_spacing))


p1 <- ggplot(aes(x=gamma,y=delta),data = model_output)  + theme_classic(base_size = 12, base_family = "") + geom_tile(aes(fill = avg_optimal_spacing))+ scale_fill_viridis(begin = 0.2,end=0.8)+
   labs(fill='Optimal spacing between reserves') +
   xlab(" ") +
   ylab(" ") +
   #ggtitle("(b) Allee effect")+
theme(legend.position="top") #+
  #annotate("text",x=0.85,y=0.1,label='(b)',col='black')
library(ggpubr)
# 
 figure=ggarrange(p1, ncol=1, nrow=1, common.legend = TRUE, legend="top")
 annotate_figure(figure,
                bottom = text_grob("Probability disturbance in 2nd patch", color = "black",
                                   hjust = 0.9,vjust=0, x = 0.7, size = 14),
                left = text_grob("Probability of successful dispersal", color = "black", rot = 90,size=14,vjust=2,hjust=0.5)
 )
```



\clearpage





## Figure 5

```{r different_objectives_code, echo=FALSE,eval=F,error=FALSE,message=FALSE,warning=FALSE}

#ptm <- proc.time()

source('../scripts/n_patch/evalFunc.R')
source('../scripts/n_patch/simulate_model_N_patches.R')

biased_disturbance_side=FALSE
biased_disturbance_rotating=FALSE

# Parameter values
num_patches=20 #15
#fraction_reserves = 0.05 # Optional code to use fraction of coastline instead of number of reserves
num_reserves = 3#floor(fraction_reserves*num_patches)
extra_patches=10
total_patches=num_patches+2*extra_patches

max_time= 100
num_trials = 100


fishing_values_vec = 1#c(0.5,0.75,1)#seq(0.3,0.9,by=0.25)
r_value_vec = 3#seq(2.5,3,by=1)
omega_value_vec = c(1.0,1.2)#seq(1.2,1.4,by=0.2)
dispersal_value_vec = c(0.7)#seq(0.1,1,by=0.1)
K = 1

disturbance_prob_vec = seq(0,0.03,0.001)
disturbance_size_vec = c(2)
disturbance_magnitude_vec = 0.9#seq(0.7,0.9,0.2)

objective_vec = c('persistence','fishing')#,'population_size')

params_list <- expand.grid(fishing_values_vec,r_value_vec,omega_value_vec,dispersal_value_vec,disturbance_prob_vec,disturbance_size_vec,disturbance_magnitude_vec,objective_vec)
params_list <- params_list[rep(seq(nrow(params_list)), each = 100), ]
names(params_list) <- c('fishing_values_vec','r_value_vec','omega_value_vec','dispersal_value_vec','disturbance_prob_vec','disturbance_size_vec','disturbance_magnitude_vec','objective_vec')

params_list$optimal_spacing = 0 
params_list$mean_objective_value = 0 
optimal_reserves_mat <- matrix(0,nrow=nrow(params_list),ncol=num_reserves)
  
for (param_index in 1:nrow(params_list)){
  fishing_value = params_list$fishing_values_vec[param_index]
  fishing_vector = rep(fishing_value,total_patches)
  r_value = params_list$r_value_vec[param_index]
  r_vector = rep(r_value, total_patches)
  omega_value = params_list$omega_value_vec[param_index]
  
  dispersal_probability_param = params_list$dispersal_value_vec[param_index]
  source('../scripts/n_patch/set_up_linear_landscape.R')
  total_patches=nrow(connectivity_matrix)
  
  disturbance_prob_param = params_list$disturbance_prob_vec[param_index]
  disturbance_size_param =  params_list$disturbance_size_vec[param_index]
  disturbance_magnitude =  params_list$disturbance_magnitude_vec[param_index]
  source('../scripts/n_patch/linear_disturbances_setup.R')
  
  objective = as.character(params_list$objective_vec[param_index])
  
 # Run code for one combination of parameters and return optimal configuration... 
  source('../scripts/n_patch/run_code_for_N_patch_model.R')
  if (length(num_near_top)==1){
    params_list$optimal_spacing[param_index] <- mean(diff(optimal_reserves)-1)
    params_list$mean_objective_value[param_index] <- -ranked_configs[1,1+num_reserves]
    optimal_reserves_mat[param_index,] <- optimal_reserves
  }else{
    # Situation where multiple configs can work
    top_configs=ranked_configs[num_near_top,1:num_reserves]
    #spacing <- apply(top_configs,1,FUN=diff) -1
    params_list$optimal_spacing[param_index] <- min(colMeans(apply(top_configs,1,FUN=diff) -1))
    params_list$mean_objective_value[param_index] <- -mean(ranked_configs[num_near_top,1+num_reserves])
    optimal_reserves_mat[param_index,] <- NA
  }
  
  print(paste(param_index,':',params_list$optimal_spacing[param_index],sep = ''))
  #print(head(ranked_configs))
  
  write.csv(params_list,file='../model_outputs/n_patch_optimal_spacing_vs_disturbance_regime_different_objectives_Fig5_temp.csv',quote = F)
}




#write.csv(params_list,file='../model_outputs/n_patch_optimal_spacing_vs_disturbance_regime_different_objectives_Fig5.csv',quote = F)
```

```{r different_objectives, echo=FALSE,eval=T,error=FALSE,message=FALSE,warning=FALSE,fig.cap='Optimal spacing between reserves (in an $n$-patch model) versus the probability of disturbance for three different objective functions. The parameter values used are: $\\delta$ = 0.7, $\\omega$ = 1.2, r = 3, and $\\mu$ = 0.9.\\label{different_objectives}'}

params_list <- read.csv(file='../model_outputs/n_patch_optimal_spacing_vs_disturbance_regime_different_objectives_Fig5_temp.csv',header=T)

# For tie-breaking, use shorter distance
#params_list$optimal_spacing[is.na(params_list$optimal_spacing)] = 0 

# Only examine omega = 1 (no Allee effect) as a reference to figure in the main manuscript.
params_list <- params_list %>%
  filter(omega_value_vec == 1.2)

# Build plot
# require(ggplot2)
# require(viridis)
# ggplot(aes(x=disturbance_prob_vec,y=optimal_spacing-1,col=objective_vec),data = params_list)  + theme_classic(base_size = 12, base_family = "") + geom_line(size=2) + coord_cartesian(xlim = c(0, 0.35))  + coord_cartesian(ylim = c(0, 2)) + theme(plot.title = element_text(size = 12, face = "plain")) +
#   labs(col='Objective') +
#   xlab("Disturbance probability") +
#   ylab("Optimal spacing between reserves") +
#   scale_color_viridis(discrete=T,alpha=0.5) #+

## New figure with error bars
require(dplyr)

params_list  <- params_list  %>%
  dplyr::group_by(disturbance_prob_vec,objective_vec) %>%
  dplyr::summarise(avg_optimal_spacing = mean(optimal_spacing),avg_optimal_spacing2.5 = as.numeric(quantile(optimal_spacing,probs=0.025)),avg_optimal_spacing97.5 = as.numeric(quantile(optimal_spacing,probs=0.975)))

require(ggplot2)
require(viridis)
require(gridExtra)
ggplot(data=params_list) +
   geom_ribbon(aes(x=disturbance_prob_vec,ymin=avg_optimal_spacing2.5,ymax=avg_optimal_spacing97.5 ,fill=as.factor(objective_vec))) + scale_fill_viridis(discrete=T,alpha=0.1,guide=F) +
   geom_line(aes(x=disturbance_prob_vec,y=avg_optimal_spacing,color=as.factor(objective_vec)),size=1.5) + scale_color_viridis(discrete = T,alpha=0.5)   + theme_classic(base_size = 14, base_family = "")   + theme(plot.title = element_text(size = 12, face = "plain")) +
  labs(color='Objective') +
  xlab("Disturbance probability") +
  ylab("Optimal spacing between reserves") 
```













\clearpage

## Figure 6 


```{r fishing_objective_model,echo=FALSE,eval=F,cache=TRUE,error=FALSE,message=FALSE,warning=FALSE}

require(viridis)
require(ggplot2)

biased_disturbance_side=FALSE
biased_disturbance_rotating=FALSE
source('../scripts/n_patch/evalFunc.R')
source('../scripts/n_patch/simulate_model_N_patches.R')

# Parameter values
num_patches=20 #15
#fraction_reserves = 0.05 # Optional code to use fraction of coastline instead of number of reserves
num_reserves = 3#floor(fraction_reserves*num_patches)
extra_patches=10
total_patches=num_patches+2*extra_patches

max_time= 100
num_trials = 100


fishing_values_vec = rep(c(1,0.75,0.5),100)#seq(0.3,0.9,by=0.25)
r_value_vec = 3#seq(2.5,3,by=1)
omega_value_vec = 1.2#seq(1.2,1.4,by=0.2)
dispersal_value_vec = c(0.7)#seq(0.1,1,by=0.1)
K = 1

disturbance_prob_vec = seq(0,0.03,0.0025)#0.0005)
disturbance_size_vec = c(2)
disturbance_magnitude_vec = 0.9#seq(0.7,0.9,0.2)

objective_vec = c('persistence')#,'fishing','population_size')

params_list <- expand.grid(fishing_values_vec,r_value_vec,omega_value_vec,dispersal_value_vec,disturbance_prob_vec,disturbance_size_vec,disturbance_magnitude_vec,objective_vec)
params_list <- params_list[rep(seq(nrow(params_list)), each = 1), ]
names(params_list) <- c('fishing_values_vec','r_value_vec','omega_value_vec','dispersal_value_vec','disturbance_prob_vec','disturbance_size_vec','disturbance_magnitude_vec','objective_vec')

params_list$optimal_spacing = 0 
params_list$mean_objective_value = 0 

optimal_reserves_mat <- matrix(0,nrow=nrow(params_list),ncol=num_reserves)
  
for (param_index in 1:nrow(params_list)){
  fishing_value = params_list$fishing_values_vec[param_index]
  fishing_vector = rep(fishing_value,total_patches)
  r_value = params_list$r_value_vec[param_index]
  r_vector = rep(r_value, total_patches)
  omega_value = params_list$omega_value_vec[param_index]
  
  dispersal_probability_param = params_list$dispersal_value_vec[param_index]
  source('../scripts/n_patch/set_up_linear_landscape.R')
  total_patches=nrow(connectivity_matrix)
  
  disturbance_prob_param = params_list$disturbance_prob_vec[param_index]
  disturbance_size_param =  params_list$disturbance_size_vec[param_index]
  disturbance_magnitude =  params_list$disturbance_magnitude_vec[param_index]
  source('../scripts/n_patch/linear_disturbances_setup.R')
  
  objective = as.character(params_list$objective_vec[param_index])
  
 # Run code for one combination of parameters and return optimal configuration... 
  source('../scripts/n_patch/run_code_for_N_patch_model.R')
  params_list$optimal_spacing[param_index] <- mean(diff(optimal_reserves)-1)
  params_list$mean_objective_value[param_index] <- -ranked_configs[1,1+num_reserves]
  optimal_reserves_mat[param_index,] <- optimal_reserves
  
  print(param_index)
  #print(paste(param_index,':',params_list$optimal_spacing[param_index],sep = ''))
}


write.csv(params_list,file='../model_outputs/n_patch_optimal_spacing_vs_disturbance_regime_different_fishing_levels_Fig6.csv',quote = F)

```

```{r fishing_objective,echo=FALSE,eval=T,cache=TRUE,error=FALSE,message=FALSE,warning=FALSE,fig.cap='Optimal spacing between reserves (in an $n$-patch model) to maximize persistence for different disturbance frequencies and fishing levels outside of reserves (fraction of population harvested in each patch). The parameter values used here are: $\\delta$ = 0.7, $\\omega$ = 1.2, r = 3, and $\\mu$ = 0.9. \\label{fishing_objective}'}

params_list <- read.csv(file='../model_outputs/n_patch_optimal_spacing_vs_disturbance_regime_different_fishing_levels_Fig6.csv',header=T)

params_list$optimal_spacing[is.na(params_list$optimal_spacing)]=0

## New figure with error bars
require(dplyr)

params_list  <- params_list  %>%
  dplyr::group_by(disturbance_prob_vec,fishing_values_vec) %>%
  dplyr::summarise(avg_optimal_spacing = mean(optimal_spacing),avg_optimal_spacing2.5 = as.numeric(quantile(optimal_spacing,probs=0.025)),avg_optimal_spacing97.5 = as.numeric(quantile(optimal_spacing,probs=0.975)))

require(ggplot2)
require(viridis)
require(gridExtra)
ggplot(data=params_list) +
   geom_ribbon(aes(x=disturbance_prob_vec,ymin=avg_optimal_spacing2.5,ymax=avg_optimal_spacing97.5 ,fill=as.factor(fishing_values_vec))) + scale_fill_viridis(discrete=T,alpha=0.1,guide=F) +
   geom_line(aes(x=disturbance_prob_vec,y=avg_optimal_spacing,color=as.factor(fishing_values_vec)),size=1.5) + scale_color_viridis(discrete = T,alpha=0.5)   + theme_classic(base_size = 14, base_family = "")   + theme(plot.title = element_text(size = 12, face = "plain")) +
  labs(color='Fishing level') +
  xlab("Disturbance frequency") +
  ylab("Optimal spacing between reserves") 
#dev.off()
```










\pagebreak

## Figure 7

```{r reserve_config_code, echo=FALSE,eval=F,error=FALSE,message=FALSE,warning=FALSE}

# For reserve configuration, I should ensure there are no ties between configs. Otherwise the ranking of configs won't be accurate...

#ptm <- proc.time()

source('../scripts/n_patch/evalFunc.R')
source('../scripts/n_patch/simulate_model_N_patches.R')

biased_disturbance_side=FALSE
biased_disturbance_rotating=FALSE

# Parameter values
num_patches=20 #15
#fraction_reserves = 0.05 # Optional code to use fraction of coastline instead of number of reserves
num_reserves = 3#floor(fraction_reserves*num_patches)
extra_patches=10
total_patches=num_patches+2*extra_patches

max_time= 100
num_trials = 100


fishing_values_vec = 1#c(0.5,0.75,1)#seq(0.3,0.9,by=0.25)
r_value_vec = 3#seq(2.5,3,by=1)
omega_value_vec = 1.2#seq(1.2,1.4,by=0.2)
dispersal_value_vec = c(0.7)#seq(0.1,1,by=0.1)
K = 1

disturbance_prob_vec = 0.01#seq(0,0.03,0.001)
disturbance_size_vec = c(2)
disturbance_magnitude_vec = 0.9#seq(0.7,0.9,0.2)

objective_vec = c('persistence')#,'population_size')

params_list <- expand.grid(fishing_values_vec,r_value_vec,omega_value_vec,dispersal_value_vec,disturbance_prob_vec,disturbance_size_vec,disturbance_magnitude_vec,objective_vec)
params_list <- params_list[rep(seq(nrow(params_list)), each = 100), ]
names(params_list) <- c('fishing_values_vec','r_value_vec','omega_value_vec','dispersal_value_vec','disturbance_prob_vec','disturbance_size_vec','disturbance_magnitude_vec','objective_vec')

params_list$optimal_spacing = 0 
params_list$mean_objective_value = 0 
optimal_reserves_mat <- matrix(0,nrow=nrow(params_list),ncol=num_reserves)
  
for (param_index in 1:nrow(params_list)){
  fishing_value = params_list$fishing_values_vec[param_index]
  fishing_vector = rep(fishing_value,total_patches)
  r_value = params_list$r_value_vec[param_index]
  r_vector = rep(r_value, total_patches)
  omega_value = params_list$omega_value_vec[param_index]
  
  dispersal_probability_param = params_list$dispersal_value_vec[param_index]
  source('../scripts/n_patch/set_up_linear_landscape.R')
  total_patches=nrow(connectivity_matrix)
  
  disturbance_prob_param = params_list$disturbance_prob_vec[param_index]
  disturbance_size_param =  params_list$disturbance_size_vec[param_index]
  disturbance_magnitude =  params_list$disturbance_magnitude_vec[param_index]
  source('../scripts/n_patch/linear_disturbances_setup.R')
  
  objective = as.character(params_list$objective_vec[param_index])
  
 # Run code for one combination of parameters and return optimal configuration... 
  source('../scripts/n_patch/run_code_for_N_patch_model.R')
  params_list$optimal_spacing[param_index] <- mean(diff(optimal_reserves)-1)
  params_list$mean_objective_value[param_index] <- -ranked_configs[1,1+num_reserves]
  optimal_reserves_mat[param_index,] <- optimal_reserves
  
  #print(paste(param_index,':',params_list$optimal_spacing[param_index],sep = ''))
  #print(head(ranked_configs))
}

#write.csv(optimal_reserves_mat,file='../model_outputs/n_patch_optimal_reserve_config_Fig7.csv',quote = F,row.names = F)
```

```{r reserve_config, echo=FALSE,eval=T,error=FALSE,message=FALSE,warning=FALSE,fig.cap='(a) Reserve locations for 20 different simulations all using the same parameter values. These are the same parameters as Fig. 5 with a set probability of disturbance of 0.01 (a value on Fig. 5 with high variability in optimal spacing) and for the persistence objective. Each R denotes the optimal placement of a reserve for each simulation. (b) Density plot of reserve locations chosen across 100 simulations. (c) Percent of simulations for each reserve configuration. Note that the middle reserve is always centered at 20, which reduces computational time.\\label{reserve_config}'}

optimal_reserves_mat <- read.csv(file='../model_outputs/n_patch_optimal_reserve_config_Fig7.csv',header=T)

layout(matrix(c(1,1,1,1,2,2,3,3,3,3,3,3), nrow = 2, ncol = 6, byrow = TRUE))
par(mar=c(0.5,0.5,0.5,0.5),oma=c(4,4,0,0))
matplot(optimal_reserves_mat[1:20,],pch='R',cex=1,ylab='Reserve location',xlab='Simulation number',ylim=c(12.5,28.5),xlim=c(0.5,20.5),col='black',las=1)
abline(h=seq(12.5,28.5,1),col='grey')
abline(v=seq(0.5,20.5,1),col='grey')
mtext('Location',side = 2,outer=F,line=3,cex=1.4)
mtext('Simulation number',side = 1,outer=F,line=3,cex=1.4)

mtext(text='(a)',side = 3,line = -1,adj = -0.1)

my_dens <- density(as.vector(as.matrix(optimal_reserves_mat)),na.rm=T)
plot(my_dens$y,my_dens$x,main='',ylab='',xlab='',xaxt='n',yaxt='n',type='l',ylim=c(12.5,28.5),frame.plot = F)

mtext(text='(b)',side = 3,line = -1,adj = 0.8)

#grid(nx = diff(c(13,28)), ny = nrow(optimal_reserves_mat), col = "lightgray", lty = "dotted",lwd = par("lwd"), equilogs = TRUE)

## BUILD A HISTOGRAM OR TABLE OF RESULTS ###

spacing <- apply(optimal_reserves_mat,1,FUN=diff) -1

df <- as.data.frame(t(spacing)) %>%
  mutate(user_A2 = pmin(V2, V3),
         V3 = pmax(V2, V3),
         V2 = user_A2) %>%
  select(-user_A2) %>%
  group_by(V2, V3) %>%
  summarise(sum = n()/100) %>%
  mutate(avg_spacing = (V3+V2)/2) %>%
  arrange(desc(sum)) %>%
  select(V2,V3,avg_spacing,sum) %>%
  na.omit()

names(df) <- c('Spacing 1','Spacing 2','Average spacing','Proportion of sims')

library(plotrix)
plot.new()
addtable2plot(0.01,0,df, 
              xpad=0, ypad=0.4,
              bty='o',
              display.rownames = FALSE, 
              display.colnames = TRUE,
              hlines = TRUE,
              vlines = TRUE)
mtext(text='(c)',side = 3,line = -6,adj = 0)
```





